Lifting CDCL to Relational Domains

### 2016-10-11 experiments.tex
experiment

\section{Experimental Results}\label{experiments}

>>>>

\section{Experimental Results}
We classify our benchmarks into two groups: {\em bounds checking}, 
{\em equivalence checking}.  We use interval, octagon, and equality 
domain for our verification task.  We analyze programs with bounded 
loops.  All loops in the program are completely unrolled before analysis.
